TrueSkill Through Time: the \proglang{Python} Package

### 2020-07-30 article.tex
TTT: correcciones a la introducción

@@

\todo[inline]{M\'as de venta de la importancia, inter\'es y potencial uso de saber la habilidad de alguien}

@@

\en{Since it is a complex variable, it is generally impossible to measure it directly (aka hidden variable).}
\es{Al ser una variable compleja, generalmente es imposible medirla directamente (aka variable oculta).}

@@

\en{Since the first generative models, proposed almost a century ago by~\cite{thurstone1927-comparativeJugement} and~\cite{zermelo1929-translation}, it is assumed that the probability of observing a positive result depends on the \emph{difference in strength} between the agent and their target, $p(\,r=1 \,|\, d_{ij}\,)$.}
\es{Ya los primeros modelos generativos, propuestos hace casi un siglo por~\cite{thurstone1927-comparativeJugement} y~\cite{zermelo1929-translation}, suponen que la probabilidad de observar un resultado positivo depende de la \emph{diferencia de escala} entre el agente y su objetivo, $p(\,r=1 \,|\, d_{ij}\,)$.}

@@

\en{In respect to their representations, the main difference is limited to the choice of one of two very similar cumulative probability distributions to define the equation~\ref{eq:pairwise-comparision}: the logistic function or the cumulative Gaussian one.}

@@

\en{Figure~\ref{fig:generative_model} provides a graphical representation of the generative model, which details the causal relationship that hidden skills ($s$) have on the observable results ($r$), through the random difference ($d$) of hidden performances ($p$).}
\es{La Figura~\ref{fig:generative_model} ofrece una representaci\'on gr\'afica del modelo generativo, en la que se detalla la relaci\'on causal que las habilidades ocultas ($s$) tienen sobre los resultados observables ($r$), a trav\'es de la diferencia aleatorias ($d$) de rendimientos ocultos ($p$).}

@@

\en{The performance that agents exhibit in each event is assumed to be random, centered around the real unknown skill $\N(p\,|\,s,\beta^2)$.}
\es{El desempe\~no que exhiben los agentes en cada evento se supone aleatorio, centrado en torno a la verdadera habilidad desconocida, $\N(s,\beta^2)$.}

@@

\en{According to the model, the results are a direct consequence of the hidden performances.}
\es{Según el modelo, los resultados son consecuencias directa de los rendimientos ocultos.}

@@

\en{Elo's methodological solution for estimating skills from results is extremely simple and astute: update the current estimate based on our surprise.}
\es{La soluci\'on metodol\'ogica de Elo para estimar habilidades a partir de resultados es extremadamente sencilla y astuta: actualizar la estimaci\'on actual en funci\'on de nuestra sorpresa.}

@@

@@

\en{As new estimates tend to generate high surprise, their presence can abruptly modify estimates that had already converged correctly.}

@@

\en{The ad-hoc solution proceeds by filtering the impact of $\Delta$ as a function of the times an agent was seen, which breaks the symmetry of equation~\ref{eq:elo_update}.}
\es{La soluci\'on ad-hoc procede filtrando el impacto de $\Delta$ en funci\'on de las veces que un agente fue visto, lo que rompe la simetr\'ia de la ecuaci\'on~\ref{eq:elo_update}.}

@@

\en{Probability Theory provides us with a consistent framework for quantifying the uncertainty of our beliefs, and to update them optimally given a model and the data~\cite{bishop2006-patternRecognitionMachineLearning}.}
\es{--.}
%
\en{The use of probabilty to represent uncertainty, however, is not an ad-hoc choice.}
\es{--.}
%
\en{Cox~\cite{cox} showed that if numerical values are used to represent degrees of belief, then a simple set of axioms encoding ``common sense'' that leads uniquely to a set of rules for manipulating degrees of belief that are equivalent to the sum and product rules of probability.}
\es{--.}

% 
% 
% 
% \cite{dangauthier2008-trueskillThroughTime}
% 
% \cite{coulom2008-wholeHistoryRating}
% 
% \cite{maystre2019-pairwise}
% 
% 
% 
% 
% TrueSkill Through Time (TTT) optar por la distribuci\'on normal y ofrece una soluci\'on \'optima.

@@

\bibliography{article}

>>>>

\en{What are the skills of the people?}
\es{¿Cuáles son las habilidades de las personas?}
\en{How difficult are the challenges they face?}
\es{¿Cuán difíciles son los desafíos que enfrentan?}
\en{How are their learning curves over time?}
\es{¿Cómo son sus curvas de aprendizaje en el tiempo?}
\en{What is the overall pattern and how variable is it?}
\es{¿Cuál es el patrón general y cuán variable es?}

@@

@@

\en{In the context of interventions, it makes it possible to avoid exposing agents to imbalanced challenges.}
\es{En las contexto de intervenciones, permite evitar exponer a los agentes a desafíos desproporcionados.}
\en{For research purposes, the ratings can be made available to subjects and the general public, stimulating interest and engagement.}
\es{Con fines de investigación, las calificaciones pueden ponerse a disposición de los sujetos y del público general, estimulando así el interés y la participación.}
\en{However, since it is a complex variable, it is generally impossible to measure it directly (aka hidden variable).}
\es{Sin embargo, al ser una variable compleja, generalmente es imposible medirla directamente (aka variable oculta).}

@@

\en{Since the first generative models, proposed almost a century ago by~\cite{thurstone1927-comparativeJugement} and~\cite{zermelo1929-translation}, it is assumed that the probability of an observed result, $r$, depends on the difference in strength, $d$, between the agent and their target.}
\es{Ya los primeros modelos generativos, propuestos hace casi un siglo por~\cite{thurstone1927-comparativeJugement} y~\cite{zermelo1929-translation}, suponen que la probabilidad de un resultado observado, $r$, depende de la diferencia de escala, $d$, entre el agente y su objetivo.}
\begin{equation} \label{eq:pairwise-comparision}
p(\,r \,|\, d_{ij}\,) 

@@

\en{The main difference in respect to their representations is limited to the choice of one of two very similar cumulative probability distributions to define the equation~\ref{eq:pairwise-comparision}: the logistic function or the cumulative Gaussian one.}

@@

\en{Figure~\ref{fig:generative_model} provides a graphical representation in which hidden skill generate observable results.}
\es{La figura~\ref{fig:generative_model} ofrece una representaci\'on gr\'afica en la que las habilidades ocultas generan los resultados observables.}

@@

\en{The causal relationship is not direct.}
\es{La relaci\'on causal no es directa.}

@@

\en{Although agents may have a specific skill at any given time ($s$), the performance ($p$) they exhibit in an event depends on an undetermined number of unknown factors, which are modeled as random noise ($\beta$), $\N(p\,|\,s,\beta^2)$.}
\es{Si bien los agentes pueden tener una habilidad específica en cada momento ($s$), el desempeño ($p$) que exhiben en cada evento depende de una cantidad indeterminada de factores desconocidos, los que se modelan como ruido aleatorio ($\beta$), $\N(p\,|\,s,\beta^2)$.}
\en{According to the model, the observed results are a direct consequence of the difference of those hidden performances, $d_{ij}=p_i - p_j$.}
\es{Según el modelo, los resultados son una consecuencias directa de la diferencia de esos rendimientos ocultos, $d_{ij}=p_i - p_j$.}
\en{An agent gets a positive result when he outperforms his opponent, $r_{ij} = (d_{ij} > 0)$.}
\es{Un agente obtiene un resultado positivo cuando supera el rendimiento de su adversario, $r_{ij} = (d_{ij} > 0)$.}

@@

\en{Elo's methodological solution extremely simple and astute: update the current estimate based on our surprise.}
\es{La soluci\'on metodol\'ogica de Elo es extremadamente sencilla y astuta: actualizar la estimaci\'on actual en funci\'on de nuestra sorpresa.}

@@

\en{Where $y_{ij}$ is $1$ for winners and $-1$ for losers, and the probability of the observed result given the a priori estimates are derived from Figure~\ref{fig:generative_model}.}
\es{Donde $y_{ij}$ es $1$ para ganadores y $-1$ para perdedores y la probabilidad del resultado observado dadas las estimaciones a priori se deriva de la figura~\ref{fig:generative_model}. }

@@

\en{As newly estimates tend to generate high surprise, their presence can abruptly modify estimates that had already converged correctly.}

@@

\en{And ad-hoc solution was proposed to breaks the symmetry of equation~\ref{eq:elo_update}: reduce the impact of $\Delta$ based on how many times the agent was already seen by the system.}
\es{Una soluci\'on ad-hoc fue propuesta para romper la simetr\'ia de la ecuaci\'on~\ref{eq:elo_update}: reducir el impacto de $\Delta$ en función de las veces que el agente ya fue visto por el sistema.}
\en{That is the role played by the famous K-factor used by FIDE.}
\es{Ese es rol que desempeña el famoso K-factor usado por la FIDE.}

@@

\en{Probability Theory provides us with a consistent framework for quantifying the uncertainty of our beliefs~\cite{bishop2006-PRML}.}
\es{La Teoría de la Probabilidad nos proporciona un marco consistente para cuantificar la incertidumbre de nuestras creencias~\citep{bishop2006-PRML}.}
%
\en{The use of probabilty to represent uncertainty is not an ad-hoc choice.}
\es{El uso de la probabilidad para representar incertidumbre no es una elección ad-hoc.}
%
% \en{Cox~\cite{cox1946-reasonableExpectation} provides a theoretical basis for using probability theory as a general logic under uncertainty.}
% \es{Cox~\cite{cox1946-reasonableExpectation} proporciona fundamentos teóricos para el uso de la teoría de la probabilidad como lógica general bajo incertidumbre.}
%
\en{Any system that represent degrees of belief by a numerical value , consistent with classical deductive logic and a set of axioms encoding commonsense reasoning, must be isomorphic to probability theory~\citep{cox1946-reasonableExpectation,vanHorn2003-guideCoxTheorem}.}
\es{Cualquier sistema que represente grados de creencia mediante un valor numérico, consistente con la lógica deductiva clásica y un conjunto de axiomas que codifican el razonamiento de sentido común,  derá ser isomórfico a la teoría de la probabilidad.}
%
\en{We can answer any questions within this framework through the two elementary rules of probability, the \emph{sum rule} and the \emph{product rule}.}
\es{Podemos responder cualquier pregunta dentro de este marco a través de las dos reglas elementales de probabilidad, la \emph{regla de la suma} y la \emph{regla del producto}.}

% , and to update them optimally given a model and the data
%
% 
% 
% 
% \cite{dangauthier2008-trueskillThroughTime}
% 
% \cite{coulom2008-wholeHistoryRating}
% 
% \cite{maystre2019-pairwise}
% 
% 
% 
% 
% TrueSkill Through Time (TTT) optar por la distribuci\'on normal y ofrece una soluci\'on \'optima.

@@

\bibliography{../../bibliografia/Gaming/gaming}
